Finding Quality Issues in SKOS Vocabularies

### 2012-03-23 background.tex
minor changes to background

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in improving the quality of SKOS vocabularies, we need to identify possible quality issues that go beyond integrity conditions defining data model consistency. Quality criteria for controlled vocabularies have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}.

@@

If we want check existing SKOS vocabularies against these criteria, we first need to identify them and determine how to evaluate them given the syntax, structure and semantics of SKOS. Since we want to provide tool support for quality checking, we must formalize these criteria into computable quality checking functions, in order to ensure consistent implementation and interpretation across tools.

>>>>

% Argue why we need to formalize them -> because otherwise they will be implemented inconsistently across applications
Thus, in order to help vocabulary and application designers in judging and improving the quality of SKOS vocabularies we must identify possible quality issues that go beyond integrity conditions defining data model consistency. We can identify such issues by examining quality criteria for controlled vocabularies that have already been discussed in standardized guidelines~\cite{ISO25964-1:2011,Z39.19:2005}, manuals~\cite{Svenonius2003,Hedden2010,Aitchison2000,Harpring2010}, case studies~\cite{Soergel1995}, and scholarly articles \cite{Coronado2009,Soergel1997,Soergel2002,Elkin2002,Kless2010}. Since we want to provide tool support for quality checking, we must formalize the identified issues into computable quality checking functions taking into account the syntax, structure and semantics of SKOS. This also ensures consistent implementation across tools.

@@
